Allee Effect and Cultural Evolution

### 2015-06-02 manuscript/draft.tex
unstable figures added

\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{amsmath}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{subcaption}

@@

Small differences in initial conditions can have major consequences in the boundaries between the unstable region and the rest of equilibria. Figure \ref{fig:unstable} shows an example with high value of social learning $z=0.4$, where two scenarios ($j$ and $k$) generate different outcomes from very close initial conditions.

\begin{figure}[h!]
  \centering
      \includegraphics[width=\textwidth]{./figures/figureUnstable}   
      \caption{Basin plot (left) and time series (right) for different initial conditions. Scenario $j$ reaches \emph{coexistence} equilibrium with initial conditions $a_0=0.39; b_0=0.99$. Scenario $k$ follows a limit cycle after 1000 time-steps with initial conditions $a_0=0.4,b_0=1.0$. This pattern is reproduced inside the orange zone of the basin plot.}
    \label{fig:unstable}
\end{figure}
